The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-06-09 doc/paper/paper2d.tex
Sky and LRG noise residual update

\author{
S. Burles\altaffilmark{\ref{MIT}}
and D. J. Schlegel\altaffilmark{\ref{Princeton}}
}
\altaffiltext{1}{Massachussetts Institute of Technology,
Boston, MA ????? \label{MIT}}
\altaffiltext{2}{Princeton University Observatory, Peyton Hall, Princeton,
NJ 08544 \label{Princeton}}

@@

@@

\begin{figure}
\figurenum{8}
\epsscale{1.0}
\plotone{spDiag2d-0412-52258_156.eps}
\figcaption{An example of 1-d sky subtraction for camera r1 on SDSS
plate 412.  The top panel shows data from 16 sky fibers corrected to airmass
unity with vertical extent equal to 67\% errors.  The solid red line shows
the best fit B-spline, with only wavelength as an independent variable.
The bottom panel shows the residual of the fit in flux counts in the sky 
spectra.
\label{fig8}
}
\end{figure}

@@

\begin{figure}
\figurenum{10}
\epsscale{1.0}
\plotone{plot_bestthru.ps}
\figcaption{Throughput of the SDSS spectroscopic system,
as measured relative to the photon density expected above
the Earth's atmospheric by an aperture of 2.5-m with a 1.3-m
obscuration by the secondary mirror baffling.  These curves
are for plate 406 observed on MJD 51817.
Solid curves are for spectrograph \#1, and dotted curves
for spectrograph \#2.
\label{fig10}
}
\end{figure}

>>>>

\author{
S. Burles\altaffilmark{\ref{MIT}}
and D. J. Schlegel\altaffilmark{\ref{Princeton}}
}
\altaffiltext{1}{Department of Physics and Kavli Institute for Astrophysics 
and Space Research, MIT, Cambridge, MA 02139 \label{MIT}}
\altaffiltext{2}{Princeton University Observatory, Peyton Hall, Princeton,
NJ 08544 \label{Princeton}}

@@

\begin{table}
\begin{tabular}{ccccccccccc}
   -5   &  -4   &   -3  &   -2  &  -1   & 0 &  1   &  2 &  3   & 4 & 5 \\
\hline
 -15.19 & -6.65 & -3.13 & -1.86 & -0.89 &  0.047  & 0.98 &  1.95 &  3.22 &  6.74 & 15.29 \\
 -15.76 & -7.31 & -3.35 & -1.95 & -0.93 &  0.041  & 1.01 &  2.04 &  3.44 &  7.40 & 15.85 \\
 -16.37 & -8.52 & -3.72 & -2.04 & -0.98 & -0.014  & 0.95 &  2.01 &  3.69 &  8.50 & 16.35 \\
 -16.77 &-10.43 & -4.43 & -2.21 & -1.05 & -0.063  & 0.93 &  2.08 &  4.30 & 10.31 & 16.65 \\
\end{tabular}
\end{table}

@@

\begin{figure}
\figurenum{8}
\epsscale{1.0}
\plotone{spDiag2d-0412-52258.ps_156}
\figcaption{An example of 1-d sky subtraction for camera r1 on SDSS
plate 412.  The top panel shows data from 16 sky fibers corrected to airmass
unity with vertical extent equal to 67\% errors.  The solid red line shows
the best fit B-spline, with only wavelength as an independent variable.
The bottom panel shows the residual of the fit in flux counts in the sky 
spectra.
\label{fig8}
}
\end{figure}

@@

\begin{figure}
\figurenum{10}
\epsscale{1.0}
\plotone{plot_bestthru.ps}
\figcaption{ Throughput of the SDSS spectroscopic system,
as measured relative to the photon density expected above
the Earth's atmospheric by an aperture of 2.5-m with a 1.3-m
obscuration by the secondary mirror baffling.  These curves
are for plate 406 observed on MJD 51817.
Solid curves are for spectrograph \#1, and dotted curves
for spectrograph \#2.
\label{fig10}
}
\end{figure}

\begin{figure}
\figurenum{11}
\epsscale{1.0}
\plottwo{plot_sky_reshist.ps}{plot_lrg_reshist.ps}
\figcaption{ Distribution of SDSS flux residuals normalized 
by the reported pipeline inverse variances.  The left plot shows
the distribution of 214 million sky pixels in reductions from both
Version 4 (upper), and Version 5 (lower) of spectro-2d.  
The best fit functional form is shown as a solid red line (see text).
The filled region shows the area between the observed version 5 distribution 
of sky flux residuals and a gaussian with identical 1-sigma confidence limits.
The right plot is the same but shows the distribution of approximately 
550 million pixels drawn from residuals with respect to best fit models of
luminous red galaxies.
\label{fig11}
}
\end{figure}
